Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data

### 2011-05-11 ltx/data_paper/DataPaper.tex
edits to Result section

As a result of the model reduction via the basis function decomposition and the decomposition of the connectivity kernel the state space model is formed
\begin{align}
 \mathbf x_{t+1}&=q(\mathbf x_t)\boldsymbol\theta+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r) \label{eq:StateEq} \\
 \mathbf y_t&=\mathbf C \mathbf x_t+\boldsymbol \epsilon_t,\label{eq:OutputEq}
\end{align}
where the nonlinear function, $q(\cdot)$, is defined as
\begin{equation}\label{eq:QmatrixForSigmapoints}
	q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
\end{equation}
\section{Estimation Algorithm}
Here we describe the problem of estimating non-linear state space neural field model using expectation-maximisation (EM) based algorithm \cite{Dempster1977,Shumway2000}. The resulting estimation process is an iterative two step procedure that converges on the maximum-likelihood estimates of the parameters. In the E-step we estimate the states $\mathbf x_t$, of the system and in the M-step we estimate the connectivity kernel parameters $\boldsymbol \theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$. Once initialized, at each iteration the sequence of smoothed state vectors is used to update the parameters by maximizing an approximate lower bound on the log likelihood function. The resulting parameters are then used when estimating the new
state vector sequence for the next iteration. The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.
\subsection{E-Step}
In the E-step the additive form of the unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation. The URTSS incorporates an unscented Kalman filter (UKF) \cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$. The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation. The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
\begin{align}\label{eq:sigmapoints1}
	\mathcal X_{0}&=\mathbf{\bar x} \\
	\mathcal X_{i}&= \mathbf{\bar x}+\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, n_x \\
	\mathcal X_{i}&=\mathbf{\bar x}-\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_{i- n_x}, \quad i= n_x+1, \dots, 2n_x 
\end{align}
where $\mathbf{\bar x}$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$, and $n_x$ is the dimension of the state space. The total number of sigma points is $2n_x+1$. The scaling parameter, $\lambda$, is defined as 
\begin{equation}\label{eq:sigmapoints3}
	\lambda=\alpha^2( n_x+\kappa) - n_x, 
\end{equation}
The positive constant $\alpha$, that determines the spread of the sigma points around $\mathbf{\bar x}$, was set to $10^{-3}$. It is typically set arbitrary small to minimise higher-order effects \cite{Haykin2001}. The other scaling parameter, $\kappa$, was set to $3-n_x$ in accordance to \cite{Julier2002a}.

@@

The correlation analysis described in Section \ref{subsec:CorrAnal} were applied to generated data in order to approximate the unknown supports of both connectivity kernel and the disturbance covariance function. In the algorithm, the unknown variables $\sigma_{\epsilon}^2$ and $\xi$ in equation () and () were set to zero in correlation analysis. By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, however, an approximate of their support can be still extracted. In fact, the estimated support for the disturbance covariance function was very accurate. The estimates of the connectivity kernel and disturbance support were normalised and thresholded for values less than 0.01. The result of the correlation analysis for the connectivity kernel is shown in Figure.\ref{fig:KernelWidthEstimation}. The red circle shows the estimated support which encompasses the non-zero values after thresholding. The estimated support of the disturbance covariance function convolved twice with the observation kernel is shown in Figure.\ref{fig:DisturbanceWidthEstimation}. By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor,$\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using the expression for Gaussian basis functions convolution.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis1.pdf}
\end{center}
\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
\label{fig:KernelWidthEstimation}
\end{figure}
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
\end{center}
\caption{{\bf Disturbance support estimation}.}
\label{fig:DisturbanceWidthEstimation}
\end{figure}
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelWidthEstimation.pdf}
\end{center}
\caption{{\bf Connectivity kernel support estimation}.}
\label{fig:KernelWidthEstimation1}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimate.pdf}
\end{center}
\caption{{\bf Connectivity kernel estimates over 100 realisations.} left: True kernel; right;Estimated kernel.}
\label{fig:KernelEstimates}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
\end{center}
\caption{{\bf Cross-section of connectivity kernel estimates over 100 realisation.} True is blue; Estimate is green; 95\% Confedence interval is red.}
\label{fig:KernelEstimateCrossSection}
\end{figure}

@@

% tables here
% ~~~~~~~~~~~
\renewcommand{\arraystretch}{1.7}
\begin{table}[!ht]
\caption{
\bf{Algorithm for the Unscented RTS Smoother}}
\label{tab:URTSSAlgorithm}
\begin{tabular}{|c|}\hline
\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
$\hat{\mathbf x}_0, \mathbf P_0$ \\
\hline
\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
\hline
\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
\hline
\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
$\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e $\\
$\mathbf M_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
\multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
$\mathbf S_t=\mathbf M_{t +1}^{b-}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
$\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\
\multicolumn{1}{|p{16cm}|}{Additional step to calculate the smoothed cross covariance matrix \cite{Sarkka2008}} \\
$\mathbf M_{t +1}^{b}=\mathbf S_t\mathbf P_{t+1}^{b}$\\
\hline
\end{tabular}
\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm. The steps are iterated 11 times for our state estimation procedure. The least squares algorithm is run after each iteration to update the parameter estimates.
\end{flushleft}
\label{tab:UKFAlgorithm}
\end{table}
 \renewcommand{\arraystretch}{1}
\newpage
\bibliographystyle{plain}
\bibliography{EMIDE}
\end{document}

>>>>

As a result of the model reduction via the basis function decomposition and the decomposition of the connectivity kernel the state space model is formed
\begin{align}
 \mathbf x_{t+1}&=q(\mathbf x_t)\boldsymbol\theta+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r) \label{eq:StateEq} \\
 \mathbf y_t&=\mathbf C \mathbf x_t+\boldsymbol \epsilon_t,\label{eq:OutputEq}
\end{align}
where the nonlinear function, $q(\cdot)$, is defined as
\begin{equation}\label{eq:QmatrixForSigmapoints}
	q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
\end{equation}
\section{Estimation Algorithm}\label{sec:EstimationAlgorithm}
Here we describe the problem of estimating non-linear state space neural field model using expectation-maximisation (EM) based algorithm \cite{Dempster1977,Shumway2000}. The resulting estimation process is an iterative two step procedure that converges on the maximum-likelihood estimates of the parameters. In the E-step we estimate the states $\mathbf x_t$, of the system and in the M-step we estimate the connectivity kernel parameters $\boldsymbol \theta$, synaptic dynamic $\xi$, disturbance variance $\sigma^2_d$ and the observation noise variance $\sigma^2_{\epsilon}$. Once initialized, at each iteration the sequence of smoothed state vectors is used to update the parameters by maximizing an approximate lower bound on the log likelihood function. The resulting parameters are then used when estimating the new
state vector sequence for the next iteration. The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.
\subsection{E-Step}
In the E-step the additive form of the unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} was used for the state estimation. The URTSS incorporates an unscented Kalman filter (UKF) \cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$. The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation. The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
\begin{align}\label{eq:sigmapoints1}
	\mathcal X_{0}&=\mathbf{\bar x} \\
	\mathcal X_{i}&= \mathbf{\bar x}+\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, n_x \\
	\mathcal X_{i}&=\mathbf{\bar x}-\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_{i- n_x}, \quad i= n_x+1, \dots, 2n_x 
\end{align}
where $\mathbf{\bar x}$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( n_x + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$, and $n_x$ is the dimension of the state space. The total number of sigma points is $2n_x+1$. The scaling parameter, $\lambda$, is defined as 
\begin{equation}\label{eq:sigmapoints3}
	\lambda=\alpha^2( n_x+\kappa) - n_x, 
\end{equation}
The positive constant $\alpha$, that determines the spread of the sigma points around $\mathbf{\bar x}$, was set to $10^{-3}$. It is typically set arbitrary small to minimise higher-order effects \cite{Haykin2001}. The other scaling parameter, $\kappa$, was set to $3-n_x$ in accordance to \cite{Julier2002a}.

@@

The correlation analysis described in Section \ref{subsec:CorrAnal} were applied to generated data in order to approximate the unknown supports of both connectivity kernel and the disturbance covariance function. In the algorithm, the unknown variables $\sigma_{\epsilon}^2$ and $\xi$ in equations () and () were set to zero in correlation analysis. By doing so, the exact shape of the kernel and disturbance covariance function cannot be inferred, this step might be considered as an initialisation for the EM algorithm, however, an approximate of their support can be still extracted. In fact, the estimated support for the disturbance covariance function was very accurate. The estimates of the connectivity kernel and disturbance support were normalised and thresholded for values less than 0.01. The result of the correlation analysis for the connectivity kernel is shown in Figure.\ref{fig:KernelWidthEstimation}. The red circle shows the estimated support which encompasses the non-zero values (black area) after thresholding. The estimated support of the disturbance covariance function convolved twice with the observation kernel is shown in Figure.\ref{fig:DisturbanceWidthEstimation}. By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor,$\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using the expression for Gaussian basis functions convolution.

The estimated supports were then applied in the EM algorithm described in Section \ref{sec:EstimationAlgorithm} to estimate the smoothed states $\hat{\mathbf x}_t^b$, the connectivity kernel weights $\boldsymbol\theta$, the synaptic dynamic $\xi$, and the hyperparameters $\sigma_{\epsilon}^2$ and $\sigma^2_d$. A $5 \times 5$ square grid of basis functions with $2.25~mm$ spacing were used to cover the estimated support where $\sigma_{\psi}^2=3.5$. This is shown in Figure.\ref{fig:KernelWidthEstimation} by blue circles, each of which representing full width at half maximum of the connectivity kernel basis functions. The true and estimated connectivity kernel over 100 realisations are shown in Figure~\ref{fig:KernelEstimates}. Cross-sections of the estimates for each run are shown in Figure~\ref{fig:KernelEstimateCrossSection}. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval. The large standard deviation is due to the high number of parameters need to be estimated.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis1.pdf}
\end{center}
\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
\label{fig:KernelWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
\end{center}
\caption{{\bf Disturbance support estimation}.}
\label{fig:DisturbanceWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimate.pdf}
\end{center}
\caption{{\bf Connectivity kernel estimates over 100 realisations.} left: True kernel; right;Estimated kernel.}
\label{fig:KernelEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
\end{center}
\caption{{\bf Cross-section of connectivity kernel estimates over 100 realisation.} True is blue; Estimate is green; 95\% Confedence interval is red.}
\label{fig:KernelEstimateCrossSection}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelWidthEstimation.pdf}
\end{center}
\caption{{\bf Connectivity kernel support estimation}.}
\label{fig:KernelWidthEstimation1}
\end{figure}

@@

@@

% tables here
% ~~~~~~~~~~~
\renewcommand{\arraystretch}{1.7}
\begin{table}[!ht]
\caption{
\bf{Algorithm for the Unscented RTS Smoother}}
\label{tab:URTSSAlgorithm}
\begin{tabular}{|c|}\hline
\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
$\hat{\mathbf x}_0, \mathbf P_0$ \\
\hline
\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
\hline
\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
\hline
\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
$\mathbf P_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t +1}^{b-})^\top+\boldsymbol \Sigma_e $\\
$\mathbf M_{t +1}^{b-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
\multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
$\mathbf S_t=\mathbf M_{t +1}^{b-}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
$\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\
\multicolumn{1}{|p{16cm}|}{Additional step to calculate the smoothed cross covariance matrix \cite{Sarkka2008}} \\
$\mathbf M_{t +1}^{b}=\mathbf S_t\mathbf P_{t+1}^{b}$\\
\hline
\end{tabular}
\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm. The steps are iterated 11 times for our state estimation procedure. The least squares algorithm is run after each iteration to update the parameter estimates.
\end{flushleft}
\label{tab:UKFAlgorithm}
\end{table}
 \renewcommand{\arraystretch}{1}
\clearpage
\newpage
\bibliographystyle{plain}
\bibliography{EMIDE}
\end{document}
